Testing the JD-R theory via O*Net definitional specification

### 2022-10-12 SIOP2023/SIOP_PROCESS.Rmd
hopefully final, Alicia is going to export "SIOP_PROCESS.pdf" as a Word document

@@

The Job Demands-Resources Theory [JD-R, @demerouti2001job] has received wide support across contexts and varied research questions. We extend the literature by 1) exploring the interaction between job demands and resources on the experience of stress using O\*Net job characteristics and 2) considering also the appraisal of demands as challenge or hindrance stressors. Here, respondents made a series of evaluations that used: direct O\*Net terminology (both descriptor and response option), and JD-R influenced ratings of challenge and hindrance stressors. Prior to a description of results, a brief overview of both the JD-R theory, the stress appraisal process, and O\*Net, is provided.

@@

The stress literature speaks to the key consideration of the way employees appraise situations or circumstances - in this case, our focus will be on work characteristics. The transactional theory of stress and coping suggests that people cognitively appraise stimuli in their environments on a continuous basis [@lazarus1984stress]. For example, two employees both informed that they need to step in and assume the responsibilities of a coworker in their absence may react differently to this job demand. One may feel quite paralyzed by the added or novel tasks, while the other may embrace it as an exciting new challenge. The terms associated with the two different appraisals of the same stressor are "challenge" and "hindrance" demands [@cavanaugh2000empirical] Challenge demands promote mastery, personal growth, and future gains. Hindrance demands, by definition, inhibit growth, learning and goal achievement. Perhaps not surprisingly, challenge stressors are typically associated with positive outcomes, whereas hindrance stressors are associated with more negative outcomes [e.g., @cavanaugh2000empirical]. Our focus here will be on the connection between hindrance demands specifically, and their association with reported stress. More specifically, our interest here is whether or not the negative hindrance association we typically observe between demands and stress can be buffered by perceived resources.

@searle2015merits note that much of our research on workplace demands is based on *a priori* classifications of demands. For instance, we assume that generally, time pressure is a negative demand on an employee. However, the stress experience, or process, described early on by @lazarus1984stress is grounded in the assumption that individual appraisals of stressors/demands vary. Their transactional theory of stress and coping states that people continuously appraise stimuli in their environments. An appraisal is the cognitive process whereby meaning is assigned to a stimulus. If a stimulus is appraised as a stressor (threat, challenge, potentially harmful), emotional distress leads to coping of some kind. This action to cope is also associated with another appraisal about the outcome itself and the process continues if the outcomes is not appraised as favorable [@lazarus1984stress]. As such, the stress appraisal process suggests that classifying a job characteristic or environmental condition as an objective demand or resource might be in error.

We next consider the empirical evidence on the subjective nature of demands and resources.  First, as hinted at above, some research suggests that job demands and resources may not be universally appraised or assigned as such. Starting with job demands, @webster2011extending  studied workload, role ambiguity, and role conflict, and found that while each could be appraised primarily as a challenge or hindrance demand, they could also simultaneously be perceived as being *both* a challenge and hindrance to different degrees. While their study not did include resources, it does document individual differences in how people may perceive stressors at work.

>Although not the primary focus of their paper, @sonnega_comparison_2018 compared self-reported (subjective) ratings of the degree of physical demands, stress, and a need for intense concentration from the Health and Retirement Study with objective ratings from O\*Net. Correlations physical demand (*r* = .52), stress (*r* = .10), and need for intense concentration (*r* = .14), again suggesting perhaps that our objective ratings of job demands (and resources) may be subject to a greater level of individual difference than we tend to think.

While the above two studies provide evidence for variability in how workers view *demands*, @schmitz_interpreting_2019 went on to further capture subjective and objective *resources* in their study of retirement.

>[Same as above]: Correlations of composite variables between subjective and objective measures for the resources of autonomy (*r* = .12. p > .01), recognition of work (*r* = .07, p > .01), and decision freedom (*r* = .08, p > .01), while significant, certainly do not reflect high levels of overlap.

We do acknowledge as well, that demands and resources are not necessarily consistent across days, or seasons, for many employees. @downes2021incorporating meta-analysis addresses this reality in depth, although a broader current elaboration is beyond the scope of this SIOP presentation.

@@

Our unique contribution in the current study is in whether or not *perceptions* of demands as hindrances or challenges are related to experienced stress, and whether or not this relationship is moderated by the presence of resources.  We do have some existing evidence that this occurs with other outcomes beyond stress. For example, @tadic2015challenge found that daily hindrance job demands were negatively related to both positive affect and engagement in a sample of primary school teachers. Daily job resources, in this sample, buffered the relationships between hindrances and affect and engagement. With the current investigation, we propose that greater perceived resources generally, as opposed to daily, would also buffer the relationship between perceived hindrance stressors and, in this, case, perceived stress. The following two predictions are made:

>*H1*. There is a positive relationship between perceived hindrance stressors and stress.

>*H2*. The relationship between mean perceived hindrances and stress will be moderated by resources such that this relationship is diminished as perceived resources increase.

@@

### Stress.

Three items taken from the Copenhagen Psychosocial Questionnaire [@burr_third_2019] captured stress (an example item is: "How often have you had problems relaxing because of your job?"). Responses were made on a 5-point scale ranging from "not at all" to "all the time". Alpha was .85 in this sample.

@@

Following data cleaning and preparation, we computed correlations among the study variables. See Table \@ref(tab:cortab). With regard to H1, which predicted a positive association between perceived hindrance stressors and stress, a small positive relationship was observed, *r* = .09, *p* < .05. Thus, "weak" support was found for H1.

@@

papaja::apa_table(table,
                  caption = "Results from a regression analysis examining the moderation of resources on the relationship between hindrance demands and stress",
                  note = "$R^2$ here",
                  landscape = FALSE,
                  escape = FALSE)

@@

Next, to explore H2, a moderated regression including hindrances, resources, and the interaction between them was done using PROCESS, version 4.1.1 [@hayes2022, see Table \@ref(tab:table)]. First, the overall regression model including mean hindrances, mean resources, and the interaction between the two variables was significant, $F_{(3, 564)}$ = 3.29, *p* = .020. The interaction between hindrance and resources (uncentered) revealed that the relationship between hindrances and stress was conditional on resources, $F_{(3, 564)}$ = 3.51, *p* = .061, providing marginal support for H2. As can be seen in Figure \@ref(fig:analyses), those with fewer resources show a much stronger positive relationship between hindrances and stress than those with more resources. As such, these results provide some evidence that resources may moderate the relationship between hindrance demands and subsequent levels of stress.

@@

The primary goal of this project was to further explore the role of perceived resources on the hindrance-stress relationship using O\*Net characteristics. While we have plentiful evidence that resources can buffer the effects of a variety of job demands on burnout, this project focuses on subjective experiences of resources and demands, focusing on demands rated as challenges and hindrances, as well as focusing on the outcome of *stress*. As expected, the results suggest a positive relationship between perceived hindrances and stress (H1). While intuitive, it is important to replicate this finding before we explore the impact of perceived resources, which arguably, is something that employers may have more leverage to control than hindrance stressors.

Second, the results serve to support the assertion that resources change the relationship between hindrances and stress such that the connection between the two is diminished as resources increase (H2). While not hypothesized or presented above, the authors did also run a regression on the *challenge*-stress relationship with resources as a moderator, with the assumption that resources would not moderate the relationship. The findings, indeed, did not indicate a moderated relationship in this case. It appears that resources are of benefit particularly when hindrances are present. In particular, the Job-demands Resources Theory [@demerouti2001job] suggests that resources would buffer the negative impact between demands and stress, and by extension, given the more traditional conceptualization of demands would be aligned with hindrance demands. 
These findings have implications worth considering. In a practical sense within the workplace, they speak to the ever present need to ensure employees have sufficient resources. Our project focused on the characteristics of one's work specifically, and in line with the literature cited above, studied the ratings or perceptions of resources and demands to account for individual differences in the way employees appraise components of their work. From a academic research standpoint, these findings integrate three related literatures: the job-demands resources, stress appraisal, and challenge-hindrance framework to examine the experience of employees across jobs - specifically, the way that resources and hindrance demands interact on the experience of stress. Results align with what all three theories/frameworks would suggest.

@@

Here, we note a number of limitations, but also provide additional directions for future research on this topic. First, while the use of O\*Net items is a strength of the paper, practical considerations limited the number of job characteristics we could include in our survey. Because our focus was on O\*Net items and our procedure was time and effort intensive, we were unable to inquire about other forms of resources (e.g., supervisor or coworker support) or demands. Thus, future study could explore these sources of support as resources and perhaps even compare the importance of various types of resources and their role in reducing the influence of hindrance stressors using O\*Net characteristics. Is it overall perceptions of having more resources that makes up for hindrances, or could it be that certain resources carry more weight? Second, our focus here was on the outcome of stress, but it may also be of value to consider what the interaction between ratings of O\*Net characteristics as resources and hindrances looks like on other outcomes of interest in a work context (e.g., commitment, motivation, engagement, intent to quit).

>>>>

abstract: |
  This project explored the role of resources on the demand-strain relationship through the lens of O\*Net derived job characteristics. When dissociating demands into challenges and hindrances, we did find tentative support for resources moderating the hindrance-strain relationship.

@@

The Job Demands-Resources Theory [JD-R, @demerouti2001job] has received wide support across contexts and varied research questions. We extend the literature by 1) exploring the interaction between job demands and resources on the experience of strain using O\*Net job characteristics and 2) considering also the appraisal of demands as challenge or hindrance stressors. Here, respondents made a series of evaluations that used: direct O\*Net terminology (both descriptor and response option), and JD-R influenced ratings of challenge and hindrance stressors. Prior to a description of results, a brief overview of both the JD-R theory, the stress appraisal process, and O\*Net, is provided.

@@

The stress/strain literature speaks to the key consideration of the way employees appraise situations or circumstances - in this case, our focus will be on work characteristics. The transactional theory of stress and coping suggests that people cognitively appraise stimuli in their environments on a continuous basis [@lazarus1984stress]. For example, two employees both informed that they need to step in and assume the responsibilities of a coworker in their absence may react differently to this job demand. One may feel quite paralyzed by the added or novel tasks, while the other may embrace it as an exciting new challenge. The terms associated with the two different appraisals of the same stressor are "challenge" and "hindrance" demands [@cavanaugh2000empirical] Challenge demands promote mastery, personal growth, and future gains. Hindrance demands, by definition, inhibit growth, learning and goal achievement. Perhaps not surprisingly, challenge stressors are typically associated with positive outcomes, whereas hindrance stressors are associated with more negative outcomes [e.g., @cavanaugh2000empirical]. Our focus here will be on the connection between hindrance demands specifically, and their association with reported strain. More specifically, our interest here is whether or not the negative hindrance association we typically observe between demands and strain can be buffered by perceived resources.

@searle2015merits note that much of our research on workplace demands is based on *a priori* classifications of demands. For instance, we assume that generally, time pressure is a negative demand on an employee. However, the stress/strain experience, or process, described early on by @lazarus1984stress is grounded in the assumption that individual appraisals of stressors/demands vary. Their transactional theory of stress and coping states that people continuously appraise stimuli in their environments. An appraisal is the cognitive process whereby meaning is assigned to a stimulus. If a stimulus is appraised as a stressor (threat, challenge, potentially harmful), emotional distress leads to coping of some kind. This action to cope is also associated with another appraisal about the outcome itself and the process continues if the outcomes are not appraised as favorable [@lazarus1984stress]. As such, the stress appraisal process suggests that classifying a job characteristic or environmental condition as an objective demand or resource might be in error.

We next consider the empirical evidence on the subjective nature of demands and resources.  First, as hinted at above, some research suggests that job demands and resources may not be universally appraised or assigned as such. Starting with job demands, @webster2011extending  studied workload, role ambiguity, and role conflict, and found that while each could be appraised primarily as a challenge or hindrance demand, they could also simultaneously be perceived as being *both* a challenge and hindrance to different degrees. While their study did not include resources, it does document individual differences in how people may perceive stressors at work. Additionally, although not the primary focus of their paper, @sonnega_comparison_2018 compared self-reported (subjective) ratings of job demands with more objective ratings of the same characteristics, finding that perceptions of characteristics may be subject to a greater level of individual difference than we tend to think.

While the above two studies provide evidence for variability in how workers view *demands*, @schmitz_interpreting_2019 went on to further capture subjective and objective *resources* in their study of retirement. They found only very small associations between subjective and objective measures for the "typically implicated" as resources variables of: 1) autonomy, 2) recognition of work, and 3) decision making freedom, again suggesting universal classification may not be appropriate. @downes2021incorporating meta-analysis addresses this reality in depth, although a broader current elaboration is beyond the scope of this SIOP presentation.

@@

Our unique contribution in the current study is in whether or not *perceptions* of demands as hindrances or challenges are related to experienced strain, and whether or not this relationship is moderated by the presence of resources.  We do have some existing evidence that this occurs with other outcomes beyond strain. For example, @tadic2015challenge found that daily hindrance job demands were negatively related to both positive affect and engagement in a sample of primary school teachers. Daily job resources, in this sample, buffered the relationships between hindrances and affect and engagement. With the current investigation, we propose that greater perceived resources generally, as opposed to daily, would also buffer the relationship between perceived hindrance stressors and, in this, case, experienced strain. The following two predictions are made:

>*H1*. There is a positive relationship between perceived hindrance stressors and strain.

>*H2*. The relationship between mean perceived hindrances and strain will be moderated by resources such that this relationship is diminished as perceived resources increase.

@@

### Strain.

Three items taken from the Copenhagen Psychosocial Questionnaire [@burr_third_2019] captured strain (an example item is: "How often have you had problems relaxing because of your job?"). Responses were made on a 5-point scale ranging from "not at all" to "all the time". Alpha was .85 in this sample.

@@

Following data cleaning and preparation, we computed correlations among the study variables. See Table \@ref(tab:cortab). With regard to H1, which predicted a positive association between perceived hindrance stressors and strain, a small positive relationship was observed, *r* = .09, *p* < .05. Thus, "weak" support was found for H1.

@@

papaja::apa_table(table,
                  caption = "Results from a regression analysis examining the moderation of resources on the relationship between hindrance demands and strain",
#                  note = "$R^2$ here",
                  landscape = FALSE,
                  escape = FALSE)

@@

Next, to explore H2, a moderated regression including hindrances, resources, and the interaction between them was done using PROCESS, version 4.1.1 [@hayes2022, see Table \@ref(tab:table)]. First, the overall regression model including mean hindrances, mean resources, and the interaction between the two variables was significant, $F_{(3, 564)}$ = 3.29, *p* = .020. The interaction between hindrance and resources (uncentered) revealed that the relationship between hindrances and strain was conditional on resources, $F_{(3, 564)}$ = 3.51, *p* = .061, providing marginal support for H2. As can be seen in Figure \@ref(fig:analyses), those with fewer resources show a much stronger positive relationship between hindrances and strain than those with more resources. As such, these results provide some evidence that resources may moderate the relationship between hindrance demands and subsequent levels of strain.

@@

The primary goal of this project was to further explore the role of perceived resources on the hindrance-strain relationship using O\*Net characteristics. While we have plentiful evidence that resources can buffer the effects of a variety of job demands on burnout, this project focuses on subjective experiences of resources and demands, focusing on demands rated as challenges and hindrances, as well as focusing on the outcome of *strain*. As expected, the results suggest a positive relationship between perceived hindrances and strain (H1). While intuitive, it is important to replicate this finding before we explore the impact of perceived resources, which arguably, is something that employers may have more leverage to control than hindrance stressors.

Second, the results serve to support the assertion that resources change the relationship between hindrances and strain such that the connection between the two is diminished as resources increase (H2). While not hypothesized or presented above, the authors did also run a regression on the *challenge*-strain relationship with resources as a moderator, with the assumption that resources would not moderate the relationship. The findings, indeed, did not indicate a moderated relationship in this case. It appears that resources are of benefit particularly when hindrances are present. In particular, the Job-demands Resources Theory [@demerouti2001job] suggests that resources would buffer the negative impact between demands and strain, and by extension, given the more traditional conceptualization of demands would be aligned with hindrance demands. 
These findings have implications worth considering. In a practical sense within the workplace, they speak to the ever present need to ensure employees have sufficient resources. Our project focused on the characteristics of one's work specifically, and in line with the literature cited above, studied the ratings or perceptions of resources and demands to account for individual differences in the way employees appraise components of their work. From a academic research standpoint, these findings integrate three related literatures: the job-demands resources, stress appraisal, and challenge-hindrance framework to examine the experience of employees across jobs - specifically, the way that resources and hindrance demands interact on the experience of strain. Results align with what all three theories/frameworks would suggest.

@@

Here, we note a number of limitations, but also provide additional directions for future research on this topic. First, while the use of O\*Net items is a strength of the paper, practical considerations limited the number of job characteristics we could include in our survey. Because our focus was on O\*Net items and our procedure was time and effort intensive, we were unable to inquire about other forms of resources (e.g., supervisor or coworker support) or demands. Thus, future study could explore these sources of support as resources and perhaps even compare the importance of various types of resources and their role in reducing the influence of hindrance stressors using O\*Net characteristics. Is it overall perceptions of having more resources that makes up for hindrances, or could it be that certain resources carry more weight? Second, our focus here was on the outcome of strain, but it may also be of value to consider what the interaction between ratings of O\*Net characteristics as resources and hindrances looks like on other outcomes of interest in a work context (e.g., commitment, motivation, engagement, intent to quit).

### 2022-10-12 SIOP2023/SIOP_PROCESS.tex
hopefully final, Alicia is going to export "SIOP_PROCESS.pdf" as a Word document

@@

The Job Demands-Resources Theory (JD-R, Demerouti et al., 2001) has received wide support across contexts and varied research questions. We extend the literature by 1) exploring the interaction between job demands and resources on the experience of stress using O*Net job characteristics and 2) considering also the appraisal of demands as challenge or hindrance stressors. Here, respondents made a series of evaluations that used: direct O*Net terminology (both descriptor and response option), and JD-R influenced ratings of challenge and hindrance stressors. Prior to a description of results, a brief overview of both the JD-R theory, the stress appraisal process, and O*Net, is provided.

@@

The stress literature speaks to the key consideration of the way employees appraise situations or circumstances - in this case, our focus will be on work characteristics. The transactional theory of stress and coping suggests that people cognitively appraise stimuli in their environments on a continuous basis (Lazarus \& Folkman, 1984). For example, two employees both informed that they need to step in and assume the responsibilities of a coworker in their absence may react differently to this job demand. One may feel quite paralyzed by the added or novel tasks, while the other may embrace it as an exciting new challenge. The terms associated with the two different appraisals of the same stressor are ``challenge'' and ``hindrance'' demands (Cavanaugh et al., 2000) Challenge demands promote mastery, personal growth, and future gains. Hindrance demands, by definition, inhibit growth, learning and goal achievement. Perhaps not surprisingly, challenge stressors are typically associated with positive outcomes, whereas hindrance stressors are associated with more negative outcomes (e.g., Cavanaugh et al., 2000). Our focus here will be on the connection between hindrance demands specifically, and their association with reported stress. More specifically, our interest here is whether or not the negative hindrance association we typically observe between demands and stress can be buffered by perceived resources.

Searle and Auton (2015) note that much of our research on workplace demands is based on \emph{a priori} classifications of demands. For instance, we assume that generally, time pressure is a negative demand on an employee. However, the stress experience, or process, described early on by Lazarus and Folkman (1984) is grounded in the assumption that individual appraisals of stressors/demands vary. Their transactional theory of stress and coping states that people continuously appraise stimuli in their environments. An appraisal is the cognitive process whereby meaning is assigned to a stimulus. If a stimulus is appraised as a stressor (threat, challenge, potentially harmful), emotional distress leads to coping of some kind. This action to cope is also associated with another appraisal about the outcome itself and the process continues if the outcomes is not appraised as favorable (Lazarus \& Folkman, 1984). As such, the stress appraisal process suggests that classifying a job characteristic or environmental condition as an objective demand or resource might be in error.

We next consider the empirical evidence on the subjective nature of demands and resources. First, as hinted at above, some research suggests that job demands and resources may not be universally appraised or assigned as such. Starting with job demands, Webster et al. (2011) studied workload, role ambiguity, and role conflict, and found that while each could be appraised primarily as a challenge or hindrance demand, they could also simultaneously be perceived as being \emph{both} a challenge and hindrance to different degrees. While their study not did include resources, it does document individual differences in how people may perceive stressors at work.

\begin{quote}
Although not the primary focus of their paper, Sonnega et al. (2018) compared self-reported (subjective) ratings of the degree of physical demands, stress, and a need for intense concentration from the Health and Retirement Study with objective ratings from O*Net. Correlations physical demand (\emph{r} = .52), stress (\emph{r} = .10), and need for intense concentration (\emph{r} = .14), again suggesting perhaps that our objective ratings of job demands (and resources) may be subject to a greater level of individual difference than we tend to think.
\end{quote}

While the above two studies provide evidence for variability in how workers view \emph{demands}, Schmitz et al. (2019) went on to further capture subjective and objective \emph{resources} in their study of retirement.

\begin{quote}
{[}Same as above{]}: Correlations of composite variables between subjective and objective measures for the resources of autonomy (\emph{r} = .12. p \textgreater{} .01), recognition of work (\emph{r} = .07, p \textgreater{} .01), and decision freedom (\emph{r} = .08, p \textgreater{} .01), while significant, certainly do not reflect high levels of overlap.
\end{quote}

We do acknowledge as well, that demands and resources are not necessarily consistent across days, or seasons, for many employees. Downes et al. (2021) meta-analysis addresses this reality in depth, although a broader current elaboration is beyond the scope of this SIOP presentation.

@@

Our unique contribution in the current study is in whether or not \emph{perceptions} of demands as hindrances or challenges are related to experienced stress, and whether or not this relationship is moderated by the presence of resources. We do have some existing evidence that this occurs with other outcomes beyond stress. For example, Tadić et al. (2015) found that daily hindrance job demands were negatively related to both positive affect and engagement in a sample of primary school teachers. Daily job resources, in this sample, buffered the relationships between hindrances and affect and engagement. With the current investigation, we propose that greater perceived resources generally, as opposed to daily, would also buffer the relationship between perceived hindrance stressors and, in this, case, perceived stress. The following two predictions are made:

\begin{quote}
\emph{H1}. There is a positive relationship between perceived hindrance stressors and stress.
\end{quote}

\begin{quote}
\emph{H2}. The relationship between mean perceived hindrances and stress will be moderated by resources such that this relationship is diminished as perceived resources increase.
\end{quote}

@@

\hypertarget{stress.}{%
\subsubsection{Stress.}\label{stress.}}

Three items taken from the Copenhagen Psychosocial Questionnaire (Burr et al., 2019) captured stress (an example item is: ``How often have you had problems relaxing because of your job?''). Responses were made on a 5-point scale ranging from ``not at all'' to ``all the time''. Alpha was .85 in this sample.

@@

Following data cleaning and preparation, we computed correlations among the study variables. See Table \ref{tab:cortab}. With regard to H1, which predicted a positive association between perceived hindrance stressors and stress, a small positive relationship was observed, \emph{r} = .09, \emph{p} \textless{} .05. Thus, ``weak'' support was found for H1.

@@

\caption{\label{tab:table}Results from a regression analysis examining the moderation of resources on the relationship between hindrance demands and stress}

\begin{tabular}{lllll}
\toprule
Component & \multicolumn{1}{c}{coeff} & \multicolumn{1}{c}{SE} & \multicolumn{1}{c}{t} & \multicolumn{1}{c}{p}\\
\midrule
Constant & 1.27 & 1.01 & 1.26 & 0.21\\
Hindrance (X) & 0.83 & 0.40 & 2.07 & 0.04\\
Resource (W) & 0.33 & 0.25 & 1.32 & 0.19\\
Hindrance x Resource & -0.19 & 0.10 & -1.87 & 0.06\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} $R^2$ here}
\end{tablenotes}

@@

Next, to explore H2, a moderated regression including hindrances, resources, and the interaction between them was done using PROCESS, version 4.1.1 (Hayes, 2022, see Table \ref{tab:table}). First, the overall regression model including mean hindrances, mean resources, and the interaction between the two variables was significant, \(F_{(3, 564)}\) = 3.29, \emph{p} = .020. The interaction between hindrance and resources (uncentered) revealed that the relationship between hindrances and stress was conditional on resources, \(F_{(3, 564)}\) = 3.51, \emph{p} = .061, providing marginal support for H2. As can be seen in Figure \ref{fig:analyses}, those with fewer resources show a much stronger positive relationship between hindrances and stress than those with more resources. As such, these results provide some evidence that resources may moderate the relationship between hindrance demands and subsequent levels of stress.

@@

The primary goal of this project was to further explore the role of perceived resources on the hindrance-stress relationship using O*Net characteristics. While we have plentiful evidence that resources can buffer the effects of a variety of job demands on burnout, this project focuses on subjective experiences of resources and demands, focusing on demands rated as challenges and hindrances, as well as focusing on the outcome of \emph{stress}. As expected, the results suggest a positive relationship between perceived hindrances and stress (H1). While intuitive, it is important to replicate this finding before we explore the impact of perceived resources, which arguably, is something that employers may have more leverage to control than hindrance stressors.

Second, the results serve to support the assertion that resources change the relationship between hindrances and stress such that the connection between the two is diminished as resources increase (H2). While not hypothesized or presented above, the authors did also run a regression on the \emph{challenge}-stress relationship with resources as a moderator, with the assumption that resources would not moderate the relationship. The findings, indeed, did not indicate a moderated relationship in this case. It appears that resources are of benefit particularly when hindrances are present. In particular, the Job-demands Resources Theory (Demerouti et al., 2001) suggests that resources would buffer the negative impact between demands and stress, and by extension, given the more traditional conceptualization of demands would be aligned with hindrance demands.
These findings have implications worth considering. In a practical sense within the workplace, they speak to the ever present need to ensure employees have sufficient resources. Our project focused on the characteristics of one's work specifically, and in line with the literature cited above, studied the ratings or perceptions of resources and demands to account for individual differences in the way employees appraise components of their work. From a academic research standpoint, these findings integrate three related literatures: the job-demands resources, stress appraisal, and challenge-hindrance framework to examine the experience of employees across jobs - specifically, the way that resources and hindrance demands interact on the experience of stress. Results align with what all three theories/frameworks would suggest.

@@

Here, we note a number of limitations, but also provide additional directions for future research on this topic. First, while the use of O*Net items is a strength of the paper, practical considerations limited the number of job characteristics we could include in our survey. Because our focus was on O*Net items and our procedure was time and effort intensive, we were unable to inquire about other forms of resources (e.g., supervisor or coworker support) or demands. Thus, future study could explore these sources of support as resources and perhaps even compare the importance of various types of resources and their role in reducing the influence of hindrance stressors using O*Net characteristics. Is it overall perceptions of having more resources that makes up for hindrances, or could it be that certain resources carry more weight? Second, our focus here was on the outcome of stress, but it may also be of value to consider what the interaction between ratings of O*Net characteristics as resources and hindrances looks like on other outcomes of interest in a work context (e.g., commitment, motivation, engagement, intent to quit).

>>>>

\abstract{%
This project explored the role of resources on the demand-strain relationship through the lens of O*Net derived job characteristics. When dissociating demands into challenges and hindrances, we did find tentative support for resources moderating the hindrance-strain relationship.
}

@@

The Job Demands-Resources Theory (JD-R, Demerouti et al., 2001) has received wide support across contexts and varied research questions. We extend the literature by 1) exploring the interaction between job demands and resources on the experience of strain using O*Net job characteristics and 2) considering also the appraisal of demands as challenge or hindrance stressors. Here, respondents made a series of evaluations that used: direct O*Net terminology (both descriptor and response option), and JD-R influenced ratings of challenge and hindrance stressors. Prior to a description of results, a brief overview of both the JD-R theory, the stress appraisal process, and O*Net, is provided.

@@

The stress/strain literature speaks to the key consideration of the way employees appraise situations or circumstances - in this case, our focus will be on work characteristics. The transactional theory of stress and coping suggests that people cognitively appraise stimuli in their environments on a continuous basis (Lazarus \& Folkman, 1984). For example, two employees both informed that they need to step in and assume the responsibilities of a coworker in their absence may react differently to this job demand. One may feel quite paralyzed by the added or novel tasks, while the other may embrace it as an exciting new challenge. The terms associated with the two different appraisals of the same stressor are ``challenge'' and ``hindrance'' demands (Cavanaugh et al., 2000) Challenge demands promote mastery, personal growth, and future gains. Hindrance demands, by definition, inhibit growth, learning and goal achievement. Perhaps not surprisingly, challenge stressors are typically associated with positive outcomes, whereas hindrance stressors are associated with more negative outcomes (e.g., Cavanaugh et al., 2000). Our focus here will be on the connection between hindrance demands specifically, and their association with reported strain. More specifically, our interest here is whether or not the negative hindrance association we typically observe between demands and strain can be buffered by perceived resources.

Searle and Auton (2015) note that much of our research on workplace demands is based on \emph{a priori} classifications of demands. For instance, we assume that generally, time pressure is a negative demand on an employee. However, the stress/strain experience, or process, described early on by Lazarus and Folkman (1984) is grounded in the assumption that individual appraisals of stressors/demands vary. Their transactional theory of stress and coping states that people continuously appraise stimuli in their environments. An appraisal is the cognitive process whereby meaning is assigned to a stimulus. If a stimulus is appraised as a stressor (threat, challenge, potentially harmful), emotional distress leads to coping of some kind. This action to cope is also associated with another appraisal about the outcome itself and the process continues if the outcomes are not appraised as favorable (Lazarus \& Folkman, 1984). As such, the stress appraisal process suggests that classifying a job characteristic or environmental condition as an objective demand or resource might be in error.

We next consider the empirical evidence on the subjective nature of demands and resources. First, as hinted at above, some research suggests that job demands and resources may not be universally appraised or assigned as such. Starting with job demands, Webster et al. (2011) studied workload, role ambiguity, and role conflict, and found that while each could be appraised primarily as a challenge or hindrance demand, they could also simultaneously be perceived as being \emph{both} a challenge and hindrance to different degrees. While their study did not include resources, it does document individual differences in how people may perceive stressors at work. Additionally, although not the primary focus of their paper, Sonnega et al. (2018) compared self-reported (subjective) ratings of job demands with more objective ratings of the same characteristics, finding that perceptions of characteristics may be subject to a greater level of individual difference than we tend to think.

While the above two studies provide evidence for variability in how workers view \emph{demands}, Schmitz et al. (2019) went on to further capture subjective and objective \emph{resources} in their study of retirement. They found only very small associations between subjective and objective measures for the ``typically implicated'' as resources variables of: 1) autonomy, 2) recognition of work, and 3) decision making freedom, again suggesting universal classification may not be appropriate. Downes et al. (2021) meta-analysis addresses this reality in depth, although a broader current elaboration is beyond the scope of this SIOP presentation.

@@

Our unique contribution in the current study is in whether or not \emph{perceptions} of demands as hindrances or challenges are related to experienced strain, and whether or not this relationship is moderated by the presence of resources. We do have some existing evidence that this occurs with other outcomes beyond strain. For example, Tadić et al. (2015) found that daily hindrance job demands were negatively related to both positive affect and engagement in a sample of primary school teachers. Daily job resources, in this sample, buffered the relationships between hindrances and affect and engagement. With the current investigation, we propose that greater perceived resources generally, as opposed to daily, would also buffer the relationship between perceived hindrance stressors and, in this, case, experienced strain. The following two predictions are made:

\begin{quote}
\emph{H1}. There is a positive relationship between perceived hindrance stressors and strain.
\end{quote}

\begin{quote}
\emph{H2}. The relationship between mean perceived hindrances and strain will be moderated by resources such that this relationship is diminished as perceived resources increase.
\end{quote}

@@

\hypertarget{strain.}{%
\subsubsection{Strain.}\label{strain.}}

Three items taken from the Copenhagen Psychosocial Questionnaire (Burr et al., 2019) captured strain (an example item is: ``How often have you had problems relaxing because of your job?''). Responses were made on a 5-point scale ranging from ``not at all'' to ``all the time''. Alpha was .85 in this sample.

@@

Following data cleaning and preparation, we computed correlations among the study variables. See Table \ref{tab:cortab}. With regard to H1, which predicted a positive association between perceived hindrance stressors and strain, a small positive relationship was observed, \emph{r} = .09, \emph{p} \textless{} .05. Thus, ``weak'' support was found for H1.

@@

\caption{\label{tab:table}Results from a regression analysis examining the moderation of resources on the relationship between hindrance demands and strain}

\begin{tabular}{lllll}
\toprule
Component & \multicolumn{1}{c}{coeff} & \multicolumn{1}{c}{SE} & \multicolumn{1}{c}{t} & \multicolumn{1}{c}{p}\\
\midrule
Constant & 1.27 & 1.01 & 1.26 & 0.21\\
Hindrance (X) & 0.83 & 0.40 & 2.07 & 0.04\\
Resource (W) & 0.33 & 0.25 & 1.32 & 0.19\\
Hindrance x Resource & -0.19 & 0.10 & -1.87 & 0.06\\
\bottomrule
\end{tabular}

@@

Next, to explore H2, a moderated regression including hindrances, resources, and the interaction between them was done using PROCESS, version 4.1.1 (Hayes, 2022, see Table \ref{tab:table}). First, the overall regression model including mean hindrances, mean resources, and the interaction between the two variables was significant, \(F_{(3, 564)}\) = 3.29, \emph{p} = .020. The interaction between hindrance and resources (uncentered) revealed that the relationship between hindrances and strain was conditional on resources, \(F_{(3, 564)}\) = 3.51, \emph{p} = .061, providing marginal support for H2. As can be seen in Figure \ref{fig:analyses}, those with fewer resources show a much stronger positive relationship between hindrances and strain than those with more resources. As such, these results provide some evidence that resources may moderate the relationship between hindrance demands and subsequent levels of strain.

@@

The primary goal of this project was to further explore the role of perceived resources on the hindrance-strain relationship using O*Net characteristics. While we have plentiful evidence that resources can buffer the effects of a variety of job demands on burnout, this project focuses on subjective experiences of resources and demands, focusing on demands rated as challenges and hindrances, as well as focusing on the outcome of \emph{strain}. As expected, the results suggest a positive relationship between perceived hindrances and strain (H1). While intuitive, it is important to replicate this finding before we explore the impact of perceived resources, which arguably, is something that employers may have more leverage to control than hindrance stressors.

Second, the results serve to support the assertion that resources change the relationship between hindrances and strain such that the connection between the two is diminished as resources increase (H2). While not hypothesized or presented above, the authors did also run a regression on the \emph{challenge}-strain relationship with resources as a moderator, with the assumption that resources would not moderate the relationship. The findings, indeed, did not indicate a moderated relationship in this case. It appears that resources are of benefit particularly when hindrances are present. In particular, the Job-demands Resources Theory (Demerouti et al., 2001) suggests that resources would buffer the negative impact between demands and strain, and by extension, given the more traditional conceptualization of demands would be aligned with hindrance demands.
These findings have implications worth considering. In a practical sense within the workplace, they speak to the ever present need to ensure employees have sufficient resources. Our project focused on the characteristics of one's work specifically, and in line with the literature cited above, studied the ratings or perceptions of resources and demands to account for individual differences in the way employees appraise components of their work. From a academic research standpoint, these findings integrate three related literatures: the job-demands resources, stress appraisal, and challenge-hindrance framework to examine the experience of employees across jobs - specifically, the way that resources and hindrance demands interact on the experience of strain. Results align with what all three theories/frameworks would suggest.

@@

Here, we note a number of limitations, but also provide additional directions for future research on this topic. First, while the use of O*Net items is a strength of the paper, practical considerations limited the number of job characteristics we could include in our survey. Because our focus was on O*Net items and our procedure was time and effort intensive, we were unable to inquire about other forms of resources (e.g., supervisor or coworker support) or demands. Thus, future study could explore these sources of support as resources and perhaps even compare the importance of various types of resources and their role in reducing the influence of hindrance stressors using O*Net characteristics. Is it overall perceptions of having more resources that makes up for hindrances, or could it be that certain resources carry more weight? Second, our focus here was on the outcome of strain, but it may also be of value to consider what the interaction between ratings of O*Net characteristics as resources and hindrances looks like on other outcomes of interest in a work context (e.g., commitment, motivation, engagement, intent to quit).
